1-generate-toys

### 2018-02-07 analysis/analyses/3-score_rules/1-generate_toys.Rmd
refactor score_rules

experiment("score_rules")
```

@@

metrics <- c("mean_R_nx", "auc_R_nx", "Q_local", "Q_global", "correlation", "isomorphic", "node_edit_score", "node_edge_edit_score", "mantel_pval", "ged")

@@

qsub_run(
  function(x) {
    library(tidyverse)
    parallel::mclapply(seq_len(nrow(toys)), function(row_id) {
      row <- dynutils::extract_row_to_list(toys, row_id)
      compare_gs_toy(.$gs, .$toy, .$gs_grouped)
    })
  },
  qsub_config = override_qsub_config(num_cores = 24),
  qsub_environment = list2env(list(compare_toy, compare_gs_toy, toys)
))

@@

metric_groups <- c("mean_R_nx"="coranking", "auc_R_nx"="coranking", "Q_local"="coranking", "Q_global"="coranking", "correlation"="correlation", "isomorphic"="isomorphic", "robbie_network_score"="robbie_network_score", "mantel_pval"="mantel", "ged"="ged") %>%
  enframe("metric_id", "metric_group_id")

>>>>

experiment("3-score_rules/1-generate_toys")
```

@@

metrics <- c("mean_R_nx", "auc_R_nx", "Q_local", "Q_global", "correlation", "edge_flip", "rf_mse", "rf_rsq")

@@

qsub_run(
  function(x) {
    library(tidyverse)
    parallel::mclapply(seq_len(nrow(toys)), function(row_id) {
      row <- dynutils::extract_row_to_list(toys, row_id)
      compare_gs_toy(.$gs, .$toy, .$gs_grouped)
    })
  },
  qsub_config = override_qsub_config(
    num_cores = 24, 
    execute_before = "source /scratch/irc/shared/dynverse/module_load_R.sh; export R_MAX_NUM_DLLS=500"
  )
)

@@

metric_groups <- c("mean_R_nx"="coranking", "auc_R_nx"="coranking", "Q_local"="coranking", "Q_global"="coranking", "correlation"="correlation", "edge_flip"="edge_flip", "rf_mse"="rf", "rf_msq"="rf") %>%
  enframe("metric_id", "metric_group_id")
